MS_metrics results

### 2023-04-06 result_sandbox.Rmd
Switching from feat_id to feature and height to area during cleanup

    select(-feat_id) %>%

@@

```{r Confusion matrices and figure, v2 clean}
dataset_versions <- c("FT2040_features", "MS3000_features")
confusion_data <- lapply(dataset_versions, function(train_set){
  full_model <- get(train_set) %>% 
    select(-feat_id) %>%
    filter(feat_class%in%c("Good", "Bad")) %>%
    mutate(feat_class=feat_class=="Good") %>%
    glm(formula=feat_class~., family = binomial)
  lapply(dataset_versions, function(test_set){
    get(test_set) %>%
      select(-feat_id) %>%
      filter(feat_class%in%c("Good", "Bad")) %>%
      mutate(pred_prob=predict(object=full_model,newdata = ., 
                               type = "response")) %>%
      mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
      select(feat_class, starts_with("pred_class")) %>%
      mutate(train_test=paste(train_set, test_set, sep = "-")) %>%
      mutate(train_test=str_remove_all(train_test, "_features")) %>%
      mutate(cross_type=ifelse(train_set==test_set, "Within", "Cross"))
  }) %>% bind_rows()
}) %>%
  bind_rows() %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  group_by(cross_type, train_test) %>%
  count(error_type) %>%
  mutate(perc=round(n/sum(n)*100)) %>%
  ungroup() %>%
  # Rename things to look nice in ggplot
  mutate(error_type=paste0("%", error_type)) %>%
  mutate(error_type=factor(error_type, paste0("%", c("TN", "TP", "FN", "FP")))) %>%
  mutate(train_test=str_replace_all(train_test, "FT2040", "Falkor")) %>%
  mutate(train_test=str_replace_all(train_test, "MS3000", "MESO")) %>%
  mutate(cross_type=paste(cross_type, "dataset", sep = "-")) %>% 
  mutate(cross_type=factor(cross_type, levels=c("Within-dataset", "Cross-dataset"))) %>%
  arrange(train_test) %>% 
  mutate(train_test=factor(train_test, levels=unique(train_test)))

@@

```{r Thresholding demo}
meso_full_model <- MS3000_features %>% 
  select(-feat_id) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)

@@

```{r Model comparison}
falkor_full_model <- FT2040_features %>% 
  select(-feat_id) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)
meso_full_model <- MS3000_features %>% 
  select(-feat_id) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)

@@

```{r feature selection and selection testing}
raw_data_params <- c("med_cor", "med_SNR")
xcms_params <- c("mean_mz", "sd_ppm", "mean_rt", "sd_rt", "mean_pw", 
                 "sd_pw", "log_mean_height", "log_sd_height", "sn", 
                 "f", "scale", "lmin", "feat_npeaks", "n_found", 
                 "samps_found", "stans_found")
all_params <- c("mean_mz", "sd_ppm", "mean_rt", "sd_rt", "mean_pw", "sd_pw",
                "log_mean_height", "log_sd_height", "sn", "f", "scale", 
                "lmin", "feat_npeaks", "n_found", "samps_found", "stans_found", 
                "med_cor", "med_SNR", "med_missed_scans", "smp_to_blk", 
                "smp_to_std", "shape_cor", "area_cor", "feat_class")
lst(all_params, raw_data_params, xcms_params) %>%
  imap(function(param_selection, param_name){
    lapply(dataset_versions, function(train_set){
      full_model <- get(train_set) %>% 
        select(feat_class, all_of(param_selection)) %>%
        filter(feat_class%in%c("Good", "Bad")) %>%
        mutate(feat_class=feat_class=="Good") %>%
        glm(formula=feat_class~., family = binomial)
      lapply(dataset_versions, function(test_set){
        get(test_set) %>%
          filter(feat_class%in%c("Good", "Bad")) %>%
          mutate(pred_prob=predict(object=full_model,newdata = ., 
                                   type = "response")) %>%
          mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
          select(feat_class, starts_with("pred_class")) %>%
          mutate(train_test=paste(train_set, test_set, sep = "-")) %>%
          mutate(train_test=str_remove_all(train_test, "_features")) %>%
          mutate(cross_type=ifelse(train_set==test_set, "Within", "Cross"))
      }) %>% bind_rows()
    }) %>% bind_rows() %>% mutate(which_params=param_name)
  }) %>% bind_rows() %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  group_by(cross_type, train_test, which_params) %>%
  count(error_type) %>%
  mutate(perc=round(n/sum(n)*100)) %>%
  ungroup() %>%
  # Rename things to look nice in ggplot
  mutate(error_type=paste0("%", error_type)) %>%
  mutate(error_type=factor(error_type, paste0("%", c("TN", "TP", "FN", "FP")))) %>%
  mutate(train_test=str_replace_all(train_test, "FT2040", "Falkor")) %>%
  mutate(train_test=str_replace_all(train_test, "MS3000", "MESO")) %>%
  mutate(cross_type=paste(cross_type, "dataset", sep = "-")) %>% 
  mutate(cross_type=factor(cross_type, levels=c("Within-dataset", "Cross-dataset"))) %>%
  arrange(train_test) %>% 
  mutate(train_test=factor(train_test, levels=unique(train_test))) %>%
  # Render the ggplot
  ggplot(aes(x=error_type, y=perc)) +
  geom_col(aes(fill=train_test), position = position_dodge()) +
  geom_text(aes(label=n, color=train_test), 
            position = position_dodge(width = 1), vjust=-0.2) +
  facet_grid(which_params~cross_type, scales = "free_x") +
  scale_y_continuous(limits = c(0, 100)) +
  scale_color_discrete("Train-test", aesthetics=c("color", "fill")) +
  theme_bw() +
  theme(axis.title = element_blank())
```

@@

```{r model stability sample size subsetting}
# Full model
meso_full_model <- MS3000_features %>% 
  select(-feat_id) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial) %>%
  broom::tidy()
set.seed(123)
meso_reps <- replicate(20, {
  meso_full_model <- MS3000_features %>% 
    slice_sample(prop = 0.5) %>%
    select(-feat_id) %>%
    filter(feat_class%in%c("Good", "Bad")) %>%
    mutate(feat_class=feat_class=="Good") %>%
    glm(formula=feat_class~., family = binomial) %>%
    broom::tidy()
}, simplify = FALSE) %>%
  bind_rows()
ggplot() +
  geom_vline(xintercept = 0) +
  geom_point(aes(x=estimate, y=term), data = meso_full_model, size=3) +
  geom_errorbar(aes(xmin=estimate-std.error*2, xmax=estimate+std.error*2, y=term), 
                data = meso_full_model, linewidth=1) +
  geom_point(aes(x=estimate, y=term), data = meso_reps, color="red") +
  facet_wrap(~term, scales = "free") +
  theme(axis.text.y=element_blank())

@@

```{r visualize PCA pixelpicking}
library(RaMS)
library(xcms)
dataset_version <- "FT2040"
output_folder <- paste0("made_data_", dataset_version, "/")
msnexp_filled <- readRDS(paste0(output_folder, "msnexp_filled.rds"))
feature_centers <- featureDefinitions(msnexp_filled) %>%
  as.data.frame() %>%
  select(mzmed, rtmed) %>%
  rownames_to_column("feat_id") %>%
  mutate(rtmed=rtmed/60) %>%
  filter(mzmed%between%c(117, 120))
msdata <- readRDS(paste0(output_folder, "msdata.rds"))
pixeldemo_msdata <- msdata$EIC2[mz%between%c(117, 120)]
interp_dt <- mapply(function(mzmed_i, rtmed_i, feat_id_i){
  interp_range <- rtmed_i+c(-0.5, 0.5)
  interp_points <- seq(interp_range[1], interp_range[2], length.out=50)
  pixeldemo_msdata[mz%between%pmppm(mzmed_i)] %>%
    split(.$filename) %>%
    lapply(function(eic_file){
      if(nrow(eic_file)>2){
        setNames(approx(eic_file$rt, eic_file$int, xout=interp_points), c("rt", "int"))
      } else {
        data.frame(rt=numeric(), int=numeric())
      }
    }) %>%
    bind_rows(.id="filename") %>%
    mutate(feature=feat_id_i)
  }, feature_centers$mzmed, feature_centers$rtmed, feature_centers$feat_id, 
  SIMPLIFY = FALSE) %>%
  bind_rows()
interp_dt %>%
  ggplot() +
  geom_line(aes(x=rt, y=int, group=filename)) +
  facet_wrap(~feature, scales="free") +
  theme(axis.text.y = element_blank(), axis.ticks.y=element_blank())

@@

```{r full PCA pixelpicking}
dataset_version <- "FT2040"
output_folder <- paste0("made_data_", dataset_version, "/")
# msnexp_filled <- readRDS(paste0(output_folder, "msnexp_filled.rds"))
# feature_centers <- featureDefinitions(msnexp_filled) %>%
#   as.data.frame() %>%
#   select(mzmed, rtmed) %>%
#   rownames_to_column("feat_id") %>%
#   mutate(rtmed=rtmed/60)
# msdata <- readRDS(paste0(output_folder, "msdata.rds"))
# interp_dt <- mapply(function(mzmed_i, rtmed_i, feat_id_i){
#   interp_range <- rtmed_i+c(-0.5, 0.5)
#   interp_points <- seq(interp_range[1], interp_range[2], length.out=50)
#   msdata$EIC2[mz%between%pmppm(mzmed_i)] %>%
#     split(.$filename) %>%
#     lapply(function(eic_file){
#       if(nrow(eic_file)>2){
#         setNames(approx(eic_file$rt, eic_file$int, xout=interp_points), c("rt", "int"))
#       } else {
#         data.frame(rt=numeric(), int=numeric())
#       }
#     }) %>%
#     bind_rows(.id="filename") %>%
#     mutate(feature=feat_id_i)
#   }, feature_centers$mzmed, feature_centers$rtmed, feature_centers$feat_id, 
#   SIMPLIFY = FALSE) %>%
#   bind_rows()
# saveRDS(interp_dt, file = paste0(output_folder, "interp_dt.rds"))
interp_dt <- readRDS(file = paste0(output_folder, "interp_dt.rds"))
interp_scaled <- interp_dt %>%
  group_by(feature, filename) %>%
  mutate(int=int/max(int)) %>%
  mutate(rt=rank(rt)) %>%
  ungroup()
pcaoutput <- interp_scaled %>%
  ungroup() %>%
  pivot_wider(names_from=feature, values_from = int) %>%
  select(which(colSums(is.na(.))==0)) %>%
  arrange(filename, rt) %>%
  select(-rt, -filename) %>%
  data.matrix() %>%
  prcomp()
pcaoutput$rotation %>%
  as.data.frame() %>%
  rownames_to_column("feature") %>%
  ggplot() +
  geom_text(aes(x=PC1, y=PC2, label=feature)) +
  theme_bw() +
  coord_fixed()

pc_features <- FT2040_features %>%
  select(feature=feat_id, feat_class) %>%
  filter(feature%in%rownames(pcaoutput$rotation)) %>%
  cbind(pcaoutput$rotation[,c("PC1", "PC2")])

@@

full_quick_model <- FT2040_features %>% 
  filter(feat_id%in%quick_classes$feature) %>%
  select(-feat_class) %>%
  left_join(quick_classes, by=c(feat_id="feature")) %>%
  select(-feat_id) %>%
  glm(formula=quick_class~., family = binomial)

mini_quick_model <- FT2040_features %>% 
  filter(feat_id%in%quick_classes$feature) %>%
  select(-feat_class) %>%
  left_join(quick_classes, by=c(feat_id="feature")) %>%
  select(quick_class, med_cor, med_SNR) %>%
  glm(formula=quick_class~., family = binomial)

>>>>

    select(-feature) %>%

@@

```{r Confusion matrices and figure, v2 clean}
dataset_versions <- c("FT2040_features", "MS3000_features")
confusion_data <- lapply(dataset_versions, function(train_set){
  full_model <- get(train_set) %>% 
    select(-feature) %>%
    filter(feat_class%in%c("Good", "Bad")) %>%
    mutate(feat_class=feat_class=="Good") %>%
    glm(formula=feat_class~., family = binomial)
  lapply(dataset_versions, function(test_set){
    get(test_set) %>%
      select(-feature) %>%
      filter(feat_class%in%c("Good", "Bad")) %>%
      mutate(pred_prob=predict(object=full_model,newdata = ., 
                               type = "response")) %>%
      mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
      select(feat_class, starts_with("pred_class")) %>%
      mutate(train_test=paste(train_set, test_set, sep = "-")) %>%
      mutate(train_test=str_remove_all(train_test, "_features")) %>%
      mutate(cross_type=ifelse(train_set==test_set, "Within", "Cross"))
  }) %>% bind_rows()
}) %>%
  bind_rows() %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  group_by(cross_type, train_test) %>%
  count(error_type) %>%
  mutate(perc=round(n/sum(n)*100)) %>%
  ungroup() %>%
  # Rename things to look nice in ggplot
  mutate(error_type=paste0("%", error_type)) %>%
  mutate(error_type=factor(error_type, paste0("%", c("TN", "TP", "FN", "FP")))) %>%
  mutate(train_test=str_replace_all(train_test, "FT2040", "Falkor")) %>%
  mutate(train_test=str_replace_all(train_test, "MS3000", "MESO")) %>%
  mutate(cross_type=paste(cross_type, "dataset", sep = "-")) %>% 
  mutate(cross_type=factor(cross_type, levels=c("Within-dataset", "Cross-dataset"))) %>%
  arrange(train_test) %>% 
  mutate(train_test=factor(train_test, levels=unique(train_test)))

@@

```{r Thresholding demo}
meso_full_model <- MS3000_features %>% 
  select(-feature) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)

@@

```{r Model comparison}
falkor_full_model <- FT2040_features %>% 
  select(-feature) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)
meso_full_model <- MS3000_features %>% 
  select(-feature) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial)

@@

```{r feature selection and selection testing}
raw_data_params <- c("med_cor", "med_SNR")
xcms_params <- c("mean_mz", "sd_ppm", "mean_rt", "sd_rt", "mean_pw", 
                 "sd_pw", "log_mean_area", "log_sd_area", "sn", 
                 "f", "scale", "lmin", "feat_npeaks", "n_found", 
                 "samps_found", "stans_found")
all_params <- c("mean_mz", "sd_ppm", "mean_rt", "sd_rt", "mean_pw", "sd_pw",
                "log_mean_area", "log_sd_area", "sn", "f", "scale", 
                "lmin", "feat_npeaks", "n_found", "samps_found", "stans_found", 
                "med_cor", "med_SNR", "med_missed_scans", "smp_to_blk", 
                "smp_to_std", "shape_cor", "area_cor", "feat_class")
lst(all_params, raw_data_params, xcms_params) %>%
  imap(function(param_selection, param_name){
    lapply(dataset_versions, function(train_set){
      full_model <- get(train_set) %>% 
        select(feat_class, all_of(param_selection)) %>%
        filter(feat_class%in%c("Good", "Bad")) %>%
        mutate(feat_class=feat_class=="Good") %>%
        glm(formula=feat_class~., family = binomial)
      lapply(dataset_versions, function(test_set){
        get(test_set) %>%
          filter(feat_class%in%c("Good", "Bad")) %>%
          mutate(pred_prob=predict(object=full_model,newdata = ., 
                                   type = "response")) %>%
          mutate(pred_class=ifelse(pred_prob>0.5, "Good", "Bad")) %>%
          select(feat_class, starts_with("pred_class")) %>%
          mutate(train_test=paste(train_set, test_set, sep = "-")) %>%
          mutate(train_test=str_remove_all(train_test, "_features")) %>%
          mutate(cross_type=ifelse(train_set==test_set, "Within", "Cross"))
      }) %>% bind_rows()
    }) %>% bind_rows() %>% mutate(which_params=param_name)
  }) %>% bind_rows() %>%
  mutate(error_type=case_when(
    feat_class=="Bad" & pred_class=="Bad" ~ "TN",
    feat_class=="Bad" & pred_class=="Good" ~ "FP",
    feat_class=="Good" & pred_class=="Bad" ~ "FN",
    feat_class=="Good" & pred_class=="Good" ~ "TP"
  )) %>%
  group_by(cross_type, train_test, which_params) %>%
  count(error_type) %>%
  mutate(perc=round(n/sum(n)*100)) %>%
  ungroup() %>%
  # Rename things to look nice in ggplot
  mutate(error_type=paste0("%", error_type)) %>%
  mutate(error_type=factor(error_type, paste0("%", c("TN", "TP", "FN", "FP")))) %>%
  mutate(train_test=str_replace_all(train_test, "FT2040", "Falkor")) %>%
  mutate(train_test=str_replace_all(train_test, "MS3000", "MESO")) %>%
  mutate(cross_type=paste(cross_type, "dataset", sep = "-")) %>% 
  mutate(cross_type=factor(cross_type, levels=c("Within-dataset", "Cross-dataset"))) %>%
  arrange(train_test) %>% 
  mutate(train_test=factor(train_test, levels=unique(train_test))) %>%
  # Render the ggplot
  ggplot(aes(x=error_type, y=perc)) +
  geom_col(aes(fill=train_test), position = position_dodge()) +
  geom_text(aes(label=n, color=train_test), 
            position = position_dodge(width = 1), vjust=-0.2) +
  facet_grid(which_params~cross_type, scales = "free_x") +
  scale_y_continuous(limits = c(0, 100)) +
  scale_color_discrete("Train-test", aesthetics=c("color", "fill")) +
  theme_bw() +
  theme(axis.title = element_blank())
```

@@

```{r model stability sample size subsetting}
# Full model
meso_full_model <- MS3000_features %>% 
  select(-feature) %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_class=feat_class=="Good") %>%
  glm(formula=feat_class~., family = binomial) %>%
  broom::tidy()
set.seed(123)
meso_reps <- replicate(20, {
  meso_full_model <- MS3000_features %>% 
    slice_sample(prop = 0.5) %>%
    select(-feature) %>%
    filter(feat_class%in%c("Good", "Bad")) %>%
    mutate(feat_class=feat_class=="Good") %>%
    glm(formula=feat_class~., family = binomial) %>%
    broom::tidy()
}, simplify = FALSE) %>%
  bind_rows()
ggplot() +
  geom_vline(xintercept = 0) +
  geom_point(aes(x=estimate, y=term), data = meso_full_model, size=3) +
  geom_errorbar(aes(xmin=estimate-std.error*2, xmax=estimate+std.error*2, y=term), 
                data = meso_full_model, linewidth=1) +
  geom_point(aes(x=estimate, y=term), data = meso_reps, color="red") +
  facet_wrap(~term, scales = "free") +
  theme(axis.text.y=element_blank())

@@

```{r visualize PCA pixelpicking}
library(RaMS)
library(xcms)
dataset_version <- "FT2040"
output_folder <- paste0("made_data_", dataset_version, "/")
msnexp_filled <- readRDS(paste0(output_folder, "msnexp_filled.rds"))
feature_centers <- featureDefinitions(msnexp_filled) %>%
  as.data.frame() %>%
  select(mzmed, rtmed) %>%
  rownames_to_column("feature") %>%
  mutate(rtmed=rtmed/60) %>%
  filter(mzmed%between%c(117, 120))
msdata <- readRDS(paste0(output_folder, "msdata.rds"))
pixeldemo_msdata <- msdata$EIC2[mz%between%c(117, 120)]
interp_dt <- mapply(function(mzmed_i, rtmed_i, feature_i){
  interp_range <- rtmed_i+c(-0.5, 0.5)
  interp_points <- seq(interp_range[1], interp_range[2], length.out=50)
  pixeldemo_msdata[mz%between%pmppm(mzmed_i)] %>%
    split(.$filename) %>%
    lapply(function(eic_file){
      if(nrow(eic_file)>2){
        setNames(approx(eic_file$rt, eic_file$int, xout=interp_points), c("rt", "int"))
      } else {
        data.frame(rt=numeric(), int=numeric())
      }
    }) %>%
    bind_rows(.id="filename") %>%
    mutate(feature=feature_i)
  }, feature_centers$mzmed, feature_centers$rtmed, feature_centers$feature, 
  SIMPLIFY = FALSE) %>%
  bind_rows()
interp_dt %>%
  ggplot() +
  geom_line(aes(x=rt, y=int, group=filename)) +
  facet_wrap(~feature, scales="free") +
  theme(axis.text.y = element_blank(), axis.ticks.y=element_blank())

@@

```{r full PCA pixelpicking}
dataset_version <- "FT2040"
output_folder <- paste0("made_data_", dataset_version, "/")
# msnexp_filled <- readRDS(paste0(output_folder, "msnexp_filled.rds"))
# feature_centers <- featureDefinitions(msnexp_filled) %>%
#   as.data.frame() %>%
#   select(mzmed, rtmed) %>%
#   rownames_to_column("feature") %>%
#   mutate(rtmed=rtmed/60)
# msdata <- readRDS(paste0(output_folder, "msdata.rds"))
# interp_dt <- mapply(function(mzmed_i, rtmed_i, feature_i){
#   interp_range <- rtmed_i+c(-0.5, 0.5)
#   interp_points <- seq(interp_range[1], interp_range[2], length.out=50)
#   msdata$EIC2[mz%between%pmppm(mzmed_i)] %>%
#     split(.$filename) %>%
#     lapply(function(eic_file){
#       if(nrow(eic_file)>2){
#         setNames(approx(eic_file$rt, eic_file$int, xout=interp_points), c("rt", "int"))
#       } else {
#         data.frame(rt=numeric(), int=numeric())
#       }
#     }) %>%
#     bind_rows(.id="filename") %>%
#     mutate(feature=feature_i)
#   }, feature_centers$mzmed, feature_centers$rtmed, feature_centers$feature, 
#   SIMPLIFY = FALSE) %>%
#   bind_rows()
# saveRDS(interp_dt, file = paste0(output_folder, "interp_dt.rds"))
interp_dt <- readRDS(file = paste0(output_folder, "interp_dt.rds"))
interp_scaled <- interp_dt %>%
  group_by(feature, filename) %>%
  mutate(int=int/max(int)) %>%
  mutate(rt=rank(rt)) %>%
  ungroup()
pcaoutput <- interp_scaled %>%
  ungroup() %>%
  pivot_wider(names_from=feature, values_from = int) %>%
  select(which(colSums(is.na(.))==0)) %>%
  arrange(filename, rt) %>%
  select(-rt, -filename) %>%
  data.matrix() %>%
  prcomp()
pcaoutput$rotation %>%
  as.data.frame() %>%
  rownames_to_column("feature") %>%
  ggplot() +
  geom_text(aes(x=PC1, y=PC2, label=feature)) +
  theme_bw() +
  coord_fixed()

# Currently broken?
pc_features <- FT2040_features %>%
  select(feature, feat_class) %>%
  filter(feature%in%rownames(pcaoutput$rotation)) %>%
  cbind(pcaoutput$rotation[,c("PC1", "PC2")])

@@

full_quick_model <- FT2040_features %>% 
  filter(feature%in%quick_classes$feature) %>%
  select(-feat_class) %>%
  left_join(quick_classes, by="feature") %>%
  select(-feature) %>%
  glm(formula=quick_class~., family = binomial)

mini_quick_model <- FT2040_features %>% 
  filter(feature%in%quick_classes$feature) %>%
  select(-feat_class) %>%
  left_join(quick_classes, by="feature") %>%
  select(quick_class, med_cor, med_SNR) %>%
  glm(formula=quick_class~., family = binomial)
